A multi-scale story of the diffusion of a new technology: the web

### 2024-06-11 presentations/web_diffusion.Rmd
path

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/shoreditch/paper/images_screenshots/screenshot_directory_website_2010.png) -->

![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/shoreditch/paper/images_screenshots/screenshot_directory_website_2010.png)

@@

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/shoreditch/paper/images_screenshots/screenshot_2010.png) -->

![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/shoreditch/paper/images_screenshots/screenshot_2010.png)

>>>>

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/shoreditch/paper/images_screenshots/screenshot_directory_website_2010.png) -->
<!-- ![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/shoreditch/paper/images_screenshots/screenshot_directory_website_2010.png) -->
![](images/screenshot_directory_website_2010.png)

@@

<!-- ![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/shoreditch/paper/images_screenshots/screenshot_2010.png) -->
<!-- ![](/Users/nw19521/Library/CloudStorage/OneDrive-UniversityofBristol/projects/shoreditch/paper/images_screenshots/screenshot_2010.png) -->
![](images/screenshot_2010.png)
